Visual Diagnostics of an Explainer Model -- Tools for the Assessment of LIME Explanations

### 2021-01-28 paper.Rnw
added GitHub link for limeaid
removed limeaid reference and specified link as urls

All runs of LIME in this paper are executed in a forked version (https://github.com/goodekat/lime) of the R package \emph{lime} (version \Sexpr{packageVersion("lime")}) by \citet{pedersen:2020}. The forked version is functionally indistinguishable from \citeauthor{pedersen:2020}'s implementation but allows us to export internal values relevant for an assessment of the explainer. The code for the diagnostic plots is stored in the R package \emph{limeaid} \citep{goode:2020}.

>>>>

All runs of LIME in this paper are executed in a forked version (\url{https://github.com/goodekat/lime}) of the R package \emph{lime} (version \Sexpr{packageVersion("lime")}) by \citet{pedersen:2020}. The forked version is functionally indistinguishable from \citeauthor{pedersen:2020}'s implementation but allows us to export internal values relevant for an assessment of the explainer. The code for the diagnostic plots is stored in the R package \emph{limeaid} available on GitHub (\url{https://github.com/goodekat/limeaid}).

### 2021-01-28 paper.tex
added GitHub link for limeaid
removed limeaid reference and specified link as urls

All runs of LIME in this paper are executed in a forked version (https://github.com/goodekat/lime) of the R package \emph{lime} (version 0.5.1) by \citet{pedersen:2020}. The forked version is functionally indistinguishable from \citeauthor{pedersen:2020}'s implementation but allows us to export internal values relevant for an assessment of the explainer. The code for the diagnostic plots is stored in the R package \emph{limeaid} \citep{goode:2020}.

>>>>

All runs of LIME in this paper are executed in a forked version (\url{https://github.com/goodekat/lime}) of the R package \emph{lime} (version 0.5.1) by \citet{pedersen:2020}. The forked version is functionally indistinguishable from \citeauthor{pedersen:2020}'s implementation but allows us to export internal values relevant for an assessment of the explainer. The code for the diagnostic plots is stored in the R package \emph{limeaid} available on GitHub (\url{https://github.com/goodekat/limeaid}).
